Empty Homes V1

### 2017-05-28 EmptyHomesV1.Rmd
Catagory plotting
Added in code that creates a catagorical variable for the percentage low-use. Inlcuded an if statment in the plotting code to do auto detection of factor variables and plots accordingly
General Cleaning of Code
I created a new function that cleaned the Ward level data to make it more easily comparable to the proper data

@@

Bexley <- read.xlsx( "Bexley Exemptions.xlsx" , colNames = FALSE) %>%
StructureData

@@

#All London With missing Boroughs
PlotMap(Southwarkinfo, AG)

 ls(pattern = "info") %>% map_df(~eval(parse(text=.x))) %>%
  PlotMap(., filter(AG, RGN15NM=="London"), filtermap = FALSE)

list.files()
```

#Semi data 
```{r}
#ward folder
setwd(SemiLondon)
list.files()

@@

#Hammersmith 
Hammersmith <- read_excel("Hammersmith.xls", skip = 1 ) %>% filter(!is.na(Ward) ) %>% 
  bind_cols(., filter(wardnames,LAD11NM == "Hammersmith and Fulham")) %>% select(-Ward) %>%
  mutate(LowUse = `Second (B)` + `Empty Unocc`+ LTE + Premium, Empty = LowUse - `Second (B)`)

Hammersmith2 <- EW2 %>% filter(LAD11NM == "Hammersmith and Fulham") %>% left_join(., select(Hammersmith, Admin_ward_code, LowUse, Empty))

HAMDAT <- AG %>% filter(LAD11NM == "Hammersmith and Fulham")%>% left_join(., select(Hammersmith, Admin_ward_code, LowUse, Empty))

@@

wardnames %>% filter(LAD11NM == "Wandsworth")

Wandsworth <- read_excel("wandsworth2.xlsx",  skip = 3 ) %>% select(1,3) %>% 
  group_by(`Ptc Wardname`) %>% summarise(Empty = sum(`Count Current Occupancy Discounts`)) %>% ungroup %>% 
  arrange(`Ptc Wardname`) %>% 
  filter(!is.na(`Ptc Wardname`)) %>% 
  bind_cols(., wardnames %>% filter(LAD11NM == "Wandsworth") %>% 
              select(Admin_ward_code)) %>%
  mutate(LowUse = Empty)

Wandsworth2 <- EW2 %>% filter(LAD11NM == "Wandsworth") %>% left_join(., select(Wandsworth, Admin_ward_code, Empty))
WANDAT <- AG %>% filter(LAD11NM == "Wandsworth")%>% left_join(., select(Wandsworth, Admin_ward_code, LowUse, Empty))

#Merton
wardnames %>% filter(LAD11NM == "Merton")
Merton <- read_excel("merton1.xlsx" )[,-2] %>%setNames(make.names(names(.))) %>% slice(-1) %>% arrange(X__1) %>%
  filter(X__1 != "Norbury", X__1!="Nightingale", X__1 !="Stonecot") %>% 
    bind_cols(., wardnames %>% filter(LAD11NM == "Merton") %>% 
              select(Admin_ward_code)) %>%
  mutate(Empty =   Disc.Class.C.Vacant.dwelling + Disc.class.C.Long.term.empty + Premium.Levy, LowUse =  Disc.Class.A.Second.home + Disc.Class.B.second.home )

MERDAT <- AG %>% filter(LAD11NM == "Merton")%>% left_join(., select(Merton, Admin_ward_code, LowUse, Empty))

test <- wardnames %>% filter(LAD11NM == "Southwark")

Southwark <- read_excel("southwark.xlsx" , skip = 1) %>% setNames(make.names(names(.))) %>% 
  filter(Ward.codes != "TOTALS") %>% select(-Ward.codes) %>%
  mutate(WARDS= na.locf(WARDS)) %>% group_by(WARDS) %>%
  summarise_all(sum, na.rm = TRUE) %>% ungroup %>%
  arrange(WARDS) %>%
    bind_cols(., wardnames %>% filter(LAD11NM == "Southwark") %>% 
              select(Admin_ward_code)) %>%
  mutate(Empty =   Unoccupied.and.furnished.lets....0. + Job.related.dwelling...50..discount + Second.Home...unoccupied.and.furnished...0.+Empty.and.unfurnished...0. + Levy.on.long.term.empty...50..Premium + Uninhabitable.Works.required....0., LowUse =  Empty )

Wandsworth2 <- EW2 %>% filter(LAD11NM == "Southwark") %>% left_join(., select(Southwark, Admin_ward_code, Empty))

SOUDAT <- AG %>% filter(LAD11NM == "Southwark")%>% left_join(., select(Southwark, Admin_ward_code, LowUse, Empty))

@@

#Kingston
test <- wardnames %>% filter(grepl("Kingston upon Thames", LAD11NM))

Kingston <- read_excel("Kingston1.xlsx"  )%>% setNames(make.names(names(.))) %>%
  arrange(X__1) %>% slice(1:16) %>%
  bind_cols(., wardnames %>% filter(LAD11NM == "Kingston upon Thames") %>% 
              select(Admin_ward_code)) %>%
  mutate(Empty = Empty...Furnished..0.. + Empty.Homes.Premium + LONG.TERM.EMPTY..0.. + Structural.Repair..0.., LowUse = Empty + X2nd.Home..0..)

KINDAT <- AG %>% filter(LAD11NM == "Kingston upon Thames")%>% left_join(., select(Kingston, Admin_ward_code, LowUse, Empty))

#TowerHamlets
test <- wardnames %>% filter(grepl("Tower", LAD11NM))

Tower <- read_excel("Towerhamlets.xlsx")[,c(1,3)] %>% 
  filter(!is.na(DiscClass)) %>%
  group_by(Ward, DiscClass) %>%
  summarise(count = n()) %>% ungroup %>%
  spread(., key =DiscClass, value = count, fill = 0 ) %>% 
  mutate(Empty = rowSums(.[,4:8]), LowUse = B+BE+Empty) %>% 
  slice(c(1:13, 15:17, 14, 18:20)) %>%
   bind_cols(., wardnames %>% filter(grepl("Tower", LAD11NM)))

TOWDAT <- AG %>% filter(grepl("Tower", LAD11NM)) %>% left_join(., select(Tower, Admin_ward_code, LowUse, Empty))

@@

Plot Map
```{r}
AG2 <- bind_rows(CHELDAT,HAMDAT, WANDAT, LAMDAT, MERDAT, 
                 SOUDAT, KINDAT, TOWDAT, GREDAT, CAMDAT, 
                 BRODAT, HARDAT, RICDAT, HILDAT, BEXDAT,
                 SUTDAT, ISLDAT, BARKDAT, BARNDAT) %>% 
  mutate(LowUsePerc = LowUse/WardHomes*100, 
         EmptyPerc = Empty/WardHomes*100,
         EmptyPercRank = percent_rank(Empty/WardHomes))

ggplot()+ geom_polygon(data=AG2, aes(long, lat, group = group, fill = EmptyPerc), 
colour = alpha("darkred", 1/2), size = 0.1) + scale_colour_gradient2() +
  labs(title = "Current London Data") +
  theme(plot.title = element_text(hjust = 0.5))+
  theme(axis.title=element_blank(),
        axis.text=element_blank(),
        axis.ticks=element_blank())

SaveFig("London.png")

AG2 %>% 
  ggplot(.)+ geom_polygon( aes(long, lat, group = group, fill =sqrt(EmptyPerc)), 
colour = alpha("darkred", 1/2), size = 0.2) + scale_colour_gradient2()

AG2 %>% 
  ggplot(.)+ geom_polygon( aes(long, lat, group = group, fill =EmptyPercRank), 
colour = alpha("darkred", 1/2), size = 0.2) + scale_colour_gradient2() +
  labs(title = "Current London Data Coloured by Percent Rank") +
  theme(plot.title = element_text(hjust = 0.5))+
  theme(axis.title=element_blank(),
        axis.text=element_blank(),
        axis.ticks=element_blank())

SaveFig("LondonPerc.png")

ggplot()+ geom_polygon(data=AG2, aes(long, lat, group = group, fill = LowUse/WardHomes), 
colour = alpha("darkred", 1/2), size = 0.2) + scale_colour_gradient2()

@@

PlotMap(Chelsea, "Chelsea")

SaveFig("RBKCLowUse.png")

@@

@@

Cornwall <- read_excel("Cornwall.xlsx", sheet=1)%>% setNames(make.names(names(.))) %>% .[,1:4] %>%
  group_by(Exemption.type, LSOA_CODE) %>% summarise(counts = n()) %>% 
  spread(key= Exemption.type, value = counts, fill = 0) %>% 
  mutate(LowUse = rowSums(.[,c(FALSE,!grepl("exempt",(names(.)[-1])))])) %>%
  left_join(., EW2, by = c("LSOA_CODE" = "ECODE")) %>% group_by(Admin_ward_code)  %>%
  mutate(LowUsePerc = LowUse/Homes, WardLowUse = sum(LowUse) ,WardLowUsePerc = WardLowUse/WardHomes) %>% ungroup

Cornwall <- Cornwall %>% left_join(., MeanWardPrice) %>% mutate(ValLow = LowUse*MeanPrice)

C2 <- Cornwall %>% 
  mutate(LowUsePerc = LowUsePerc*100,
         WardLowUsePerc = WardLowUsePerc*100) %>% 
  left_join(., AG, by = c("LSOA_CODE" = "lsoa11cd"))

ggplot(C2, aes(long, lat, group = group, fill = WardLowUsePerc))+ 
  geom_polygon(colour = alpha("black", 1/4), size = 0.2) + 
  scale_fill_gradient2(low = "blue", mid = "white", high = "red", midpoint = mean(C2$WardLowUsePerc, na.rm = TRUE))+
    theme(plot.title = element_text(hjust = 0.5))+
    theme(axis.title=element_blank(),
        axis.text=element_blank(),
        axis.ticks=element_blank())+ 
  labs(title = "Low Use Homes in the County of Cornwall", 
       fill="Percentage")     
SaveFig("Cornwall.png")

@@

 Cornwall %>% ggplot(., aes(y=MedianPrice, x= WardLowUsePerc )) + geom_point() +
   labs(title = "Mean Price vs Low Use % by ward in Cornwall",
        x = "Low Use Percentage by Ward", 
        y = "Mean Price") +
  theme(plot.title = element_text(hjust = 0.5)) + 
    annotate("text", 
             label = paste0("Correlation =", signif(CornCor[1,1],2)), 
             x = 0.35 , y = 2.5e5, size = 5) +
   geom_smooth(method = "lm", se = FALSE)#+
#   coord_cartesian(xlim=c(0,0.2), ylim= c(1e5, 3.5e+5))
SaveFig("CornCor.png")

@@

test <-read_excel(file.path(RegionsComp, "Region Yorkshire and The Humber",
                "KINGSTON UPON HULL%2c CITY OFDISCOUNTSLSOA.XLSX"))[-c(c(1:6)),1:4] %>%
  CleanData(.)

>>>>

test <- Lambethinfo %>% select(LowUsePerc, WardLowUsePerc, LowuseClass, WardLowuseClass)

@@

Bexleyinfo <- read.xlsx( "Bexley Exemptions.xlsx" , colNames = FALSE) %>%
StructureData

@@

#All London With missing Boroughs
PlotMap(Lambethinfo, AG)

 ls(pattern = "info") %>% map_df(~eval(parse(text=.x))) %>%
  PlotMap(., filter(AG, RGN15NM=="London"), filtermap = FALSE)
SaveFig("LondonCont.png")

 ls(pattern = "info") %>% map_df(~eval(parse(text=.x))) %>%
  PlotMap(., filter(AG, RGN15NM=="London"), variable = "LowuseClass", filtermap = FALSE)
SaveFig("LondonDisc.png")

#Semi data

The LSOA will be assigned empty and low use homes by percentage

```{r}
#ward folder
setwd(SemiLondon)
list.files()

@@

#Hammersmith 
Hammersmithinfo <- read_excel("Hammersmith.xls", skip = 1 ) %>% filter(!is.na(Ward) ) %>% 
  bind_cols(., filter(wardnames,LAD11NM == "Hammersmith and Fulham")) %>% select(-Ward) %>%
  mutate(LowUse = `Second (B)` + `Empty Unocc`+ LTE + Premium, Empty = LowUse - `Second (B)`) %>%
  SemiDataStructure

@@

Wandsworthinfo <- read_excel("wandsworth2.xlsx",  skip = 3 ) %>% select(1,3) %>% 
  group_by(`Ptc Wardname`) %>% summarise(Empty = sum(`Count Current Occupancy Discounts`)) %>% ungroup %>% 
  arrange(`Ptc Wardname`) %>% 
  filter(!is.na(`Ptc Wardname`)) %>% 
  bind_cols(., wardnames %>% filter(LAD11NM == "Wandsworth") %>% 
              select(Admin_ward_code)) %>%
  mutate(LowUse = Empty) %>%
  SemiDataStructure

#Merton

Mertoninfo <- read_excel("merton1.xlsx" )[,-2] %>%setNames(make.names(names(.))) %>% slice(-1) %>% arrange(X__1) %>%
  filter(X__1 != "Norbury", X__1!="Nightingale", X__1 !="Stonecot") %>% 
    bind_cols(., wardnames %>% filter(LAD11NM == "Merton") %>% 
              select(Admin_ward_code)) %>%
  mutate(Empty =   Disc.Class.C.Vacant.dwelling + Disc.class.C.Long.term.empty + Premium.Levy, LowUse =  Disc.Class.A.Second.home + Disc.Class.B.second.home ) %>%
  SemiDataStructure

@@

#Kingston

Kingstoninfo <- read_excel("Kingston1.xlsx"  )%>% setNames(make.names(names(.))) %>%
  arrange(X__1) %>% slice(1:16) %>%
  bind_cols(., wardnames %>% filter(LAD11NM == "Kingston upon Thames") %>% 
              select(Admin_ward_code)) %>%
  mutate(Empty = Empty...Furnished..0.. + Empty.Homes.Premium + LONG.TERM.EMPTY..0.. + Structural.Repair..0.., LowUse = Empty + X2nd.Home..0..) %>%
  SemiDataStructure

#TowerHamlets
Towerinfo <- read_excel("Towerhamlets.xlsx")[,c(1,3)] %>% 
  filter(!is.na(DiscClass)) %>%
  group_by(Ward, DiscClass) %>%
  summarise(count = n()) %>% ungroup %>%
  spread(., key =DiscClass, value = count, fill = 0 ) %>% 
  mutate(Empty = rowSums(.[,4:8]), LowUse = B+BE+Empty) %>% 
  slice(c(1:13, 15:17, 14, 18:20)) %>%
   bind_cols(., wardnames %>% filter(grepl("Tower", LAD11NM))) %>%
  SemiDataStructure

@@

Plot Map
```{r}

 ls(pattern = "info") %>% map_df(~eval(parse(text=.x))) %>%
  PlotMap(., filter(AG, RGN15NM=="London"), 
          filtermap = FALSE,
          title = "Map of London with all current data")
SaveFig("LondonCont.png")

 ls(pattern = "info") %>% map_df(~eval(parse(text=.x))) %>%
  PlotMap(., filter(AG, RGN15NM=="London"), variable = "LowuseClass", 
          filtermap = FALSE, 
          title = "Map of London by low-use class")
SaveFig("LondonDisc.png")

@@

PlotMap(Chelseainfo, AG, title = "Low-use homes in Kensington and Chelsea")
SaveFig("RBKCLowUse.png")

PlotMap(CoLinfo, AG, title = "Low-use homes in the city of London")
SaveFig("CoLLowUse.png")

PlotMap(Lambethinfo, AG, title = "Low-use homes in Lambeth")
SaveFig("LamLowUse.png")

@@

ChelseaCor <- Chelseainfo %>% 
  summarise(x =cor(MedianPrice, WardLowUsePerc, use = 'complete.obs'))

 Chelseainfo %>% ggplot(., aes(y=MedianPrice, x= WardLowUsePerc )) + geom_point() +
   labs(title = "Median Price vs Low Use % by ward in RBKC",
        x = "Low Use Percentage by Ward", 
        y = "Median Price") +
  theme(plot.title = element_text(hjust = 0.5)) + 
    annotate("text", 
             label = paste0("Correlation = ", 
             signif(ChelseaCor[1,1],2)), 
             x = 5 , y = 3.5e5, size = 5) +
   geom_smooth(method = "lm", se = FALSE)
SaveFig("ChelseaCor.png")

@@

Cornwall <- read_excel("Cornwall.xlsx", sheet=1)%>% setNames(make.names(names(.))) %>% .[,1:4] %>%
  StructureData(lowuse = c(2,23:28))

PlotMap(Cornwall, AG, title = "Lowuse in Cornwall")
SaveFig("Cornwall.png")

read_excel("Cornwall.xlsx", sheet=1)%>% setNames(make.names(names(.))) %>% .[,1:4] %>%
  StructureData(lowuse = c(2,7:16, 21:28) ) %>%
  PlotMap(., AG,title = "all empties")

@@

 Cornwall %>% ggplot(., aes(y=MedianPrice, x= WardLowUsePerc )) + geom_point() +
   labs(title = "Mean Price vs Low Use % by ward in Cornwall",
        x = "Low Use Percentage by Ward", 
        y = "Mean Price") +
  theme(plot.title = element_text(hjust = 0.5)) + 
    annotate("text", 
             label = paste0("Correlation = ", signif(CornCor[1,1],2)), 
             x = 5 , y = 3.5e5, size = 5) +
   geom_smooth(method = "lm", se = FALSE)
SaveFig("CornCor.png")

@@

test <-read_excel(file.path(RegionsComp, "Region Yorkshire and The Humber",
                "KINGSTON UPON HULL%2c CITY OFDISCOUNTSLSOA.XLSX"))[-c(c(1:6)),1:4] %>%
  StructureData(.)
